---
Author: "Student Name"
title: "Assignment 2"
output: html_notebook
---
##SET UP
set working directory and load dataset
```{r}
myDataLocation <- "Path to data location on your computer"

setwd(myDataLocation)

IBM_data <- read.csv(file = "IBM_data.csv", header = TRUE)
```
##SET UP
Next load favorite packages
```{r}
library(dplyr) 
library(ggplot2)
library(ggformula)
library(supernova)
library(lsr)
library(mosaic)
```
##NOTES - I do not want a word document. Use R Markdown and perform your work and writeup here. Maintain APA stype formatting for the parts where you are actually writing something down. 

##ACTIVITY
**Part 1. Purpose**
Describe three interesting hypotheses that you could ask with this data for one outcome (attrition, performance, age, etc.) variable. 

Each hypothesis should have one explanatory variable. **Your explanatory variables must include one quantitative variable and one categorical variable.** Write the relationships in word equations and give your interpretation for each.

#You may use the below or create one of your own Example Hypotheses: 
1) What is the average age (quant) of the people in each department (cat)? 
2) What is the hourly rate (quant) for m/f employees by job role (cat)?
3) Can we identify a trend between age (quant) and job satisfaction(cat, num)?
4) Can we identify trends between employee attrition (cat) and age(quant) or salary (quant) or percent salary hike (quant)?


**Part2: Data**
a) Describe the characteristics (demographics) of your sample (see Week One Assignment). 
    -This is where you are reviewing each variable and understanding whether it is cat or quant, and made       up of numeric or str characters.
```{r}
#This is where code goes 
```
b) Create a categorized variable from a quantitative variable that describes something about your sample, and include it in your description. (perhaps age or salary or categories) 
```{r}
#This is where code goes 
```
c) Describe the criteria you used to define the categories. 
```{r}
#This is where code goes 
```
d) Report descriptive statistics **str(myData$variable)** and five-number summaries **fav_stats(myData$quantvar)** of your (1) outcome and (3) explanatory variables.
    - remember favstats is only for numerics (quant vars), and tally() or boxplots can be used for categorical vars.
```{r}
#This is where code goes 
```
e) Remove outliers and describe how and why you removed them.
```{r}
#This is where code goes
```
**Part3: Visualizations**
Create histograms, boxplots, jitter plots, or scatter plots, depending on whether they are quantitative/categorical and explanatory/outcome, that would best visualize your three hypotheses (one plot each). Use proper conventions and labels for your axis’s. Use smooth density overlays and facet_grids when applicable. **Be sure to use titles, axis labels, and legend labels if applicable.**
```{r}
#This is where code goes
```
**Part4: Reults**
Based on your plots and analysis of the data, 
  a. Describe what the bars/points, x-axis, and y-axis mean in your plots. Be sure to give context by         referencing your variables (what they mean!). Reference the figures you created in Q3 as you discuss      them.
```{r}
#This is where code goes 
```
  b. What can you say from the distributions of your variables about their different characteristics     
     (e.g., shape, center, spread, kurtosis, skew, and outliers)?
```{r}
#This is where code goes 
```  
  c. What are your conclusions about the relationships between the outcome variable with the explanatory       variables for your three hypotheses?
```{r}
#This is where code goes 
```
  d. What can you say about the population sampled, and the data-generating process?
```{r}
#This is where code goes 
```
Generalize your inferences from this sample to the intended population using APA style reporting.
####Enter response here in this Markdown chunk####









**Step 5: Implications**
For one of your hypotheses, give interesting examples that could result in measurement error, sampling error, and mistakes. What are other variables in the dataset that could help explain variation in your outcome? What other variables, not in the dataset, could also explain variation in the outcome? How so? Are there any confounding variables that may change your interpretations?
####Enter response here in this Markdown chunk####






 **Step 6: Discussion**
To recap, how could your analysis report be used by an employer? What do you believe is the practical significance of your analysis? Why is it important to understand the nature and circumstances that could influence the relationship between your outcome and explanatory variables?
####Enter response here in this Markdown chunk####
